\framework: Morphology-based Entity and Relational Entity Extraction Framework for Arabic

### 2018-04-12 tex/merf/TALMajor/abstract.tex
changes to answer, colors, and some reviewers addressed

Rule-based techniques and tools to extract entities and relational entities from documents allow users to specify desired entities using natural language questions, finite state automata, regular expressions, structured query language statements, or proprietary scripts.
These techniques and tools require expertise in linguistics and programming and they lack support of Arabic {\em morphological analysis} which is key to process Arabic text.
In this work, we present \framework; a morphology-based entity and relational entity extraction framework for Arabic text.
\framework provides a friendly interface where the user, with basic knowledge of linguistic features and regular expressions, defines {\em tag types} and interactively associates them with regular expressions defined over Boolean formulae.
Boolean formulae range over matches of Arabic morphological features, and synonymity features.
Users define relations with tuples of subexpression matches and can associate code actions with subexpressions.
\framework computes feature matches, regular expression matches, and constructs entities and relational entities from the user-defined relations.
We evaluated our work with several case studies and compared with existing application-specific techniques.
The results show that \framework requires shorter development time and effort compared to existing techniques and produces reasonably accurate results within a reasonable overhead in run time.

>>>>

Rule-based techniques and tools to extract entities and relational entities from documents allow users to specify desired entities using natural language questions, finite state automata, regular expressions, structured query language statements, or proprietary scripts.
These techniques and tools require expertise in linguistics and programming.
\major{
They lack support of Arabic {\em morphological analysis} which is key to 
process Arabic text.
}
In this work, we present \framework; a morphology-based entity and relational entity extraction framework for Arabic text.
\framework provides a friendly interface where the user, with basic knowledge of linguistic features and regular expressions, defines tag types and interactively associates them with regular expressions defined over Boolean formulae.
Boolean formulae range over matches of Arabic morphological features, and synonymity features.
Users define relations with tuples of subexpression matches and can associate code actions with subexpressions.
\framework computes feature matches, regular expression matches, and constructs entities and relational entities from the user-defined relations.
We evaluated our work with several case studies and compared with existing application-specific techniques.
The results show that \framework requires shorter development time and effort compared to existing techniques and produces reasonably accurate results within a reasonable overhead in run time.

### 2018-04-12 tex/merf/TALMajor/answer/Reviewer1.comments.tex
In progress: merging motivation with section 3
changes to answer, colors, and some reviewers addressed

\answer{
  Thank you. 
}

@@

  \item \label{Review1.1} 
The authors chose to use formal notation to describe the 
objects manipulated by the software. 
This make things rigouros but the notations are sometimes heavy.
\answer{
  We clarified the following notations.... 
  The new notations appear in Sectioon AA in teh paper. 
}

@@

\item \label{Review1.3} 
The system is evaluated and compared to four other systems for 
tasks of Information Extraction.
the data used for the evaluation is not clearly described, 
did you have a manual gold annotation of all the data ?
\answer{
We have to look at the test data for the paper. 
}

\item \label{Review1.4} 
what is the size of the evaluation data ? 
did you have a train and a test data set ?
\answer{
No training... testing yes. 
}

\item \label{Review1.5} 
how did you compute the time for the implementation of rules 
with the other system (one of the tasks needed 2 month of work 
!! is it really 2 acutal months of work or is it the period of 
time during which the development has been done)
\answer{
A research assistant 6 hours course work and 14 hours 
teaching duties performed the task in two months. 
}

\item \label{Review1.5} 
more should be said about the evaluation methodology.
\answer{
We added a methodology section. 
}

\item \label{Review1.6}
you say nothing about the availability of the system, 
is it distributed ? free ? what kind of licence ?
\answer{
Available online on github, with GPL license. 
}

>>>>

\noindent\answer{
  Thank you. 
}

@@

  \item \label{Review1.1} 
The authors chose to use formal notation to describe the 
objects manipulated by the software. 
This make things rigouros but the notations are sometimes heavy.

\answer{
  We clarified the following notations.... 
  The new notations appear in Section AA in the paper. 
}

@@

\itodo{
Add two sentences in the paper to say what isA does. 
}

\item \label{Review1.3} 
The system is evaluated and compared to four other systems for 
tasks of Information Extraction.
the data used for the evaluation is not clearly described, 
did you have a manual gold annotation of all the data ?

\answer{
Manual annotators inspected the outcome of the tools and provided 
corrections where tools made mistakes. 
The corrections form the manual gold annotation that we
compared against. 
We indicate that in the Results Section. 
}
\itodo{
  Add teh above to teh results section. 
}

\item \label{Review1.4} 
what is the size of the evaluation data ? 
did you have a train and a test data set ?

\answer{
  \framework does not require training. 
  It is an interactive tool where the user provides the formulae, expressions,
    relation tuples and the associated code. 
  The user inspects the results and refines the model accordingly. 
  The testing set is available with the tool. 
}

\itodo{
  Ameen will get the size from teh files and provide. 
}

\item \label{Review1.5} 
how did you compute the time for the implementation of rules 
with the other system (one of the tasks needed 2 month of work 
!! is it really 2 acutal months of work or is it the period of 
time during which the development has been done)
more should be said about the evaluation methodology.

\answer{
A research assistant 6 hours course work and 14 hours 
teaching duties performed the task in two months. 
}
\itodo{
Add this to the results/evaluation
}

\item \label{Review1.5}
you say nothing about the availability of the system, 
is it distributed ? free ? what kind of licence ?

\answer{
\framework is open source and available online. We modified the
contributions in the Introduction Section to indicate that. 
}

### 2018-04-12 tex/merf/TALMajor/answer/Reviewer3.comments.tex
changes to answer, colors, and some reviewers addressed

\begin{enumerate}[leftmargin=0mm,label=\bfseries CommentR3.\arabic*]
\item \label{Review.3.1}
As a reader, It wasn't very easy to followup with the writing 
style. I needed to return back to ``Saref'' and ``MATAr'' papers 
to understand the terminology used.
\answer{
  We added a background section with definitions... 
}

First, I think we can ask 
"What would a researcher reading this paper need to know?", the answer would be:

\item \label{Review.3.2}
1- ``What is new in MERF?''. and this was clear for the reader 
    which is mainly
    a)(entity and relational entity extraction).
    b) defining tag of words based on a synonymic relation
\answer{
  ...
}

\item \label{Review.3.3}
2- ``How to use MERF?''
(you can have more explanations in your appendex and could have 
``help'' button in your API. This part was also relatively 
clear for the reader.
\answer{
  ... 
}

\item \label{Review.3.4}
3- The most important part is ``how MERF was built 
(methodology)?''. but I found this part was not very clear.
\answer{
  We added a methodology section...
}

4-and for sure ``how it was evaluated and good results discussion''. hich needs more attention.
\answer{
  We added subsection Results.X to discuss the evaluation 
  strategy. 
  We also added extended the discussion section... 
}

The following are some detailed recomendations:

@@

\item \label{Review.3.6}
2- in the introduction you illusterated a target example, 
so why don you need the Motivation section. 
What about if combine both.
\answer{
  Thank you. We combine both as motivation and we include that
  as a subsection of the introduction. 
}

\item \label{Review.3.7}
In addition, at page 9 ``the edges and internal nodes are text, 
morphology-based, and word distance based relational entities'' 
is not clear.
\answer{
  We rephrase the sentence to read ... 
}

\item \label{Review.3.8}
please always define your terminology before using it and 
provide examples. suggest the ``formula" was not so clear. 
I suggest using regular grammar insted since you are using 
regular expression and the match tree can be considered as 
parse tree.
\answer{
  We use formula to define predicates that range over 
  the morphological features. 
  We consider the matches of the formulae as tokens/tags (maybe
  we call them tag types.)
  We then use regular expressions (maybe we should use rules). 
  ... 
  We modify the paper by adopting the suggested terminology: 
  rule for regular expression and parse tree for match tree. 
}

\item \label{Review.3.9}
2- Section ``Existing annotation and entity extraction tools” 
need to be with section 6 or section 6 need to be combined 
with it in as one section but leaving the comparision to 
the analysis section.
\answer{
  We thank the reviewer for the comment. 
  We moved Section 1.1 to Section 6. 
}

\item \label{Review.3.10}
3- Section Background:Morphological analysis, 
the definition explaned in page 9 did not match table 1 at page 7.
\answer{
  We fix the definition to reflect that a prefix (and an suffix)
  could be a concatenation of other prefixes. 
}

\item \label{Review.3.11}
4- Section 5 can be combined with section 2. 
you can introduce the user friendly interface using the 
specified example. 
Section 2 seemed not very imporatnt as stand alone section.
\answer{
  We merged Section 2 with Section 1. 
  We move Section 5 to become Section 2 so that it follows 
  the motivation directly. 
}

5- Section MERF/

@@

\answer{
We split Figure 3 into three Figures and provide explanations
for both. 
a. Arabic Text (Consider MBBF as input coming fro another figure) ----> Tags.
b. Rest of the figure... 
c. RTC + Diff. + Visualizatiin 
}

\item \label{Review.3.13}
b) Syn$^k$ is nicely explaned but I did not recognize it as 
your own idea. if this is your idea to use English translation 
as a pivot to extract Arabic synonyms then it needs to have 
more focus because I think this is new.
\answer{
Up to our knowledge, we introduced the idea. 
We highlight the concept more in the paper. 
}

\item \label{Review.3.14}
what is $2^{gloss}$ and $2^{s}$?
\answer{
  The power sets of... We clarify that in the paper. 
}

\item \label{Review.3.15}
please to make it easier for the reader to followup, 
let the example in figure 4 also be defined as the formula 
variables. w,{u},..so on
\answer{
  We do that now.
}

\item \label{Review.3.16}
c) In MRE section,page 10, $k <=7$ why? 
\answer{
  Computational reasons ... say it in the paper. 
}

\item \label{Review.3.17}
also, A belongs-to F , A is a morphological feature, 
then how CF belongs-to A. A is defined as one item not a set.
\answer{
Thank you. This is a mistake. We corrected that in teh paper to 
read as follows... 
}

\item \label{Review.3.18}
MRT definition is not clear.
\answer{
We clarify the definition of MRE in the paper. 
}

\item \label{Review.3.19}
"MRE" and "user defined relations and actions " sections 
were hard to be understood.
\answer{
We rewrote both sections... 
}

\item \label{Review.3.20}
MREF simulator: please provide examples soon after the 
definitions to make it easier for the reader. 
The reader can be lost so fast within the variable definitions. 
\answer{
We provide running examples with the definitions....
}

\item \label{Review.3.21}
for each word you are computing all the formulas values, 
so the comlexity is O(text length X number of formulas), 
what is the range of number of formulas ?
\answer{
  ... 
  The complexity is (\#solutions for all words) times 
  (\#number of user defined formulae). 
  We provide no limit on that.
  Practically, users define up to 10 formula. 
  We include this discussion in the paper .. 
}

\item \label{Review.3.22}
you are using R as tuple defining relation, 
then bellow you used it as set of feature vectors for the text. 
This is confusing the reader. 
I needed to read the definition in MATAr paper to understand 
what R is.
\answer{
  We cleaned the definitions... 
}

\item \label{Review.3.23}
d) In general, what was the data structure used? 
how would the annotated text be saved?
\answer{
  We used XXX data structures... 
}

\item \label{Review.3.24}
6- At section Results, comparing the development time 
did not strength the work. 
This is my first time to see researchers compare their 
algorithm in term of line of code and developing time. 
I would suggest comparing the algorithm complexity 
(linear , exponential, etc), and comparing how fast a user can 
accomplish similar jobs in the different applications. 
This can be done by assiging similar corpus annotation job 
and information extraction while computeing time needed by 
the user 
``as a survey like comparison for qualitative evaluation''. 
you can search for ``user interface system evaluation''. 
There is huristic evaluation where you give weight for job 
complexity and record time needed to complete it.

\answer{
By development time we meant the time it required the 
users to build an automated annotator similar to 
the MERF based annotator. 
We clarify that in the paper ...

We conducted a survey as requested and we compare the 
manual annotation time without MERF to the annotation
time with MERF. 
}

\item \label{Review.3.24}
Also, comparison with previous work done by (Zaraket ) 
in different vesion seems like comparing with your previous work 
only and not with others. 
It would be nice to compare others work too because user 
interface could be introduced in different view.
\answer{
 ?????   
}

\item \label{Review.3.24}
What is the data size of your evaluation? 
I couldn't find how presion and recal was counted. 
you mentioned books but did you covered all the text in those 
books ? and how long was it? you can define it in term of 
number of relation extracted , tags added, expesion processed, 
sentences,..etc
\answer{
  We include more information about the data and 
  the evaluation process... 
}

\item \label{Review.3.24}
7- At section Discussion, I strongly urge you to discuss 
WHY the precission and recall have these values.
\answer{
We extend the discussion section to discuss ... 
}

\item \label{Review.3.25}
Clarity:  
It was not very clear how the work was done 
``Methodology part''. 
Having ``Existing annotation and entity extraction tools'' 
under unspecified section is misleading the reader.

\item \label{Review.3.25}
unnumbered subsections was misleading me as a reader. 
\answer{
  Fixed. CLS file was not compatible with arabtex package. 
}

\item \label{Review.3.25}
table 1 at page 7 while referring to it only at page 9. 
I think it need to be closer to where it was mentioned in the text. 
\answer{
  Done.
}

\item \label{Review.3.25}
``MERF regular expressions support operators such as concatenation, zero or one, zero or more, one or more, up to $M$” what is M? 
it could be for example 0<=M<=|chunk| Section 4 “MERF”please add “Methedology”
\answer{
  $M$ is ... we clarified that in the paper. 
}

\item \label{Review.3.25}
Correctness: 
1- in the abstract, the sentence ``These techniques and 
tools require expertise in linguistics and programming and 
lack support of Arabic morphological analysis which is key to 
process Arabic text''
gives the meaning that ``it require lack support'' so I think it 
needs to be reformulated 
\answer{
  We rephrased the sentence as requested. 
}

\item \label{Review.3.25}
2-``defines tag types and''.// unify the font here and 
many other places in the paper. 
for example look at words(,correct,commercial)
\answer{
  Emphasize ... 
}

\item \label{Review.3.25}
Originality:  
This work will contribute in facilitating Arabic corpus 
annotation, if it was made available for other researchers in 
the field to access and use it, although there is no 
referencing to where it can be accessed. 
this is an improvement of a per-existing work ``MATAr: Morphology-based Tagger for Arabic''
\answer{
  The work is available on github... 
}

>>>>

\begin{enumerate}[leftmargin=0mm,label=\bfseries CommentR3.\arabic*]
\item \label{Review.3.1}
As a reader, It wasn't very easy to followup with the writing 
style. 
I needed to return back to ``Saref'' and ``MATAr'' papers 
to understand the terminology used.

\answer{
  We added a background section with definitions... 
}

\item \label{Review.3.2}
First, I think we can ask 
``What would a researcher reading this paper need to know?", the answer would be:

1- ``What is new in MERF?''. and this was clear for the reader 
    which is mainly
    a)(entity and relational entity extraction).
    b) defining tag of words based on a synonymic relation

\answer{
  Thank you. 
}

\item \label{Review.3.3}
2- ``How to use MERF?''
(you can have more explanations in your appendex and could have 
``help'' button in your API. This part was also relatively 
clear for the reader.

\answer{
  Thank you. We added a tutorial/video demo... 
}

\item \label{Review.3.4}
3- The most important part is ``how MERF was built 
(methodology)?''. but I found this part was not very clear.

\answer{
  We added a methodology section...
}

\itodo{
  We should the following sections.
    1. \framework methodology: diagram with its description, and the 
    reference to the example +...
    2. \framework supporting tools: the current \framework section
    3. \framework GUI: remain as is

  Look for high level stuff in the (2) and (3) sections that can move
    into (1).

    When this is done go over the answers to make sure the references
    to answers in the paper are accurate.
}

4-and for sure ``how it was evaluated and good results discussion''. 
which needs more attention.

\answer{
  We added subsection Results.X to discuss the evaluation 
  strategy. 
  We also added extended the discussion section... 
}

\itodo{same answer from Reviewer 1}

The following are some detailed recommendations:

@@

\item \label{Review.3.6}
2- in the introduction you illustrated a target example, 
so why don you need the Motivation section. 
What about if combine both.

\answer{
  Thank you. We combine both as motivation and we include that
  as a subsection of the introduction. 
}

\item \label{Review.3.7}
In addition, at page 9 ``the edges and internal nodes are text, 
morphology-based, and word distance based relational entities'' 
is not clear.

\answer{
  We rephrased the sentence in the paper to read as follows. 
  \begin{quote}
The leaf nodes of the match trees are matches to formulae and the internal nodes represent roots to sub-expression matches.
  \end{quote}
}

\item \label{Review.3.8}
please always define your terminology before using it and 
provide examples. suggest the ``formula" was not so clear. 
I suggest using regular grammar instead since you are using 
regular expression and the match tree can be considered as 
parse tree.

\answer{
  We use formula to define predicates that range over 
  the morphological features. 
  We consider the matches of the formulae as tokens/tags (maybe
  we call them tag types.)
  We then use regular expressions (maybe we should use rules).

  We modify the paper by adopting the suggested terminology: 
  rule for regular expression and parse tree for match tree. 
}

\itodo{
Lets use regular grammar and introduce that with similarity to antler.
MRE becomes a macro maybe a good acronym is morphology based regular grammar rule 
MRGR. 
}

\item \label{Review.3.9}
2- Section ``Existing annotation and entity extraction tools” 
need to be with section 6 or section 6 need to be combined 
with it in as one section but leaving the comparison to 
the analysis section.

\answer{
We merged the content of Subsection 1.1 with the Related Work 
Section~\ref{sec:related}. 
}

\item \label{Review.3.10}
3- Section Background:Morphological analysis, 
the definition explained in page 9 did not match table 1 at page 7.

\answer{
  We modified the definition to indicate that the prefix and suffix 
  and the corresponding tags maybe concatenations of smaller prefix,
  suffix and tags.  
}

\item \label{Review.3.11}
4- Section 5 can be combined with section 2. 
you can introduce the user friendly interface using the 
specified example. 
Section 2 seemed not very imporatnt as stand alone section.

\answer{
  We introduced a new Methodology Section~\ref{sec:methodology} and
  we moved the content of old Section 2 to it. 
}

@@

\answer{
We split Figure 3 (the flow diagram figure) 
into three Figures and provide explanations
for each. 
a. Arabic Text (Consider MBF as input coming from another figure) ----> Tags.
b. Rest of the figure... 
c. RTC + Diff. + Visualizatiin 
}

\itodo{
  Edit the figure and split it  and refer to the (a), (b) and (c) in the paper. 
}

\item \label{Review.3.13}
b) Syn$^k$ is nicely explanied but I did not recognize it as 
your own idea. if this is your idea to use English translation 
as a pivot to extract Arabic synonyms then it needs to have 
more focus because I think this is new.

\answer{
Up to our knowledge, we introduced the idea. 
We claim that now as a novelty and a contribution in the introduction
and we rephrase the beginning of Section~\ref{sec:synk}. 
}

\item \label{Review.3.14}
what is $2^{gloss}$ and $2^{s}$?

\answer{
The notation $2^s$ denotes the power set of set $s$ which is 
the set of all subsets of $s$. 
We clarify that in the paper. 
}

\item \label{Review.3.15}
please to make it easier for the reader to followup, 
let the example in figure 4 also be defined as the formula 
variables. w,{u},..so on

\answer{
We modified the paragraph explaining the example to refer
to the formula variables. 
}

\item \label{Review.3.16}
c) In MRE section,page 10, $k <=7$ why?

\answer{
  We answer this by introducing the following in the paper.
  \begin{quote}
  We limit $k$ to a maximum of $7$ since we practically noticed that 
  (1) values above $7$ introduce significant semantic noise and
  (2) the computation is expensive without a bound. 
  \end{quote} 
}

\item \label{Review.3.17}
also, A belongs-to F , A is a morphological feature, 
then how CF belongs-to A. A is defined as one item not a set.

\answer{
This is a mistake. We corrected that in the paper to 
read as follows... 
}

\itodo{
  Ameen please find where you fixed this and say it here. 
}

\item \label{Review.3.18}
MRT definition is not clear.

\answer{
We clarify the definition of MRE in the paper. 
}

\itodo{
  Clarify the definition. 
}

\item \label{Review.3.19}
"MRE" and "user defined relations and actions " sections 
were hard to be understood.

\answer{
We rewrote both sections... 
}

\itodo{
  Figure our something to do/say.
}

\item \label{Review.3.20}
MREF simulator: please provide examples soon after the 
definitions to make it easier for the reader. 
The reader can be lost so fast within the variable definitions.

\answer{
We provide running examples with the definitions....
}
\itodo{
  Color them and say where they are. 
}

\item \label{Review.3.21}
for each word you are computing all the formulas values, 
so the complexity is O(text length X number of formulas), 
what is the range of number of formulas ?

\answer{
  The complexity is the number of morphological solutions 
  times the number of user defined formulae. 
  We provide no limit on the number of user defined formulae.
  Practically, in our case studies we did not need to defined
  more than 10 formulae per case study. 
  We include this discussion in the Results Section of the paper. 
}

\itodo{
  Add that to the Results. 
}

\item \label{Review.3.22}
you are using R as tuple defining relation, 
then bellow you used it as set of feature vectors for the text. 
This is confusing the reader. 
I needed to read the definition in MATAr paper to understand 
what R is.

\answer{
  We cleaned the definitions... 
}

\itodo{
  Ameen: highlight the changes and refer to them please. 
}

\item \label{Review.3.23}
d) In general, what was the data structure used? 
how would the annotated text be saved?

\answer{
  We used XXX data structures... 
}

\itodo{
  Ameen: JSON add that as a paragraph in the methodology section. 
}

\item \label{Review.3.24}
6- At section Results, comparing the development time 
did not strength the work. 
This is my first time to see researchers compare their 
algorithm in term of line of code and developing time. 
I would suggest comparing the algorithm complexity 
(linear , exponential, etc), and comparing how fast a user can 
accomplish similar jobs in the different applications. 
This can be done by assigning similar corpus annotation job 
and information extraction while computing time needed by 
the user 
``as a survey like comparison for qualitative evaluation''. 
you can search for ``user interface system evaluation''. 
There is heuristic evaluation where you give weight for job 
complexity and record time needed to complete it.

\answer{
Our evaluation is a survey based evaluation.
Users used \framework to define their \framework based annotators. 
Users also built finite state transducer based annotators to 
perform the same tasks on the same corpora. 
We measured and reported the time needed by both.

We also performed manual annotation to construct the correctness 
benchmark.
We did that by correcting the automated annotations of both annotators
for the benchmark corpora. 
That alone took much more time than the time it took to develop and run
the \framework annotators.

We clarify that in the beginning of the Results Section ~\ref{sec:results}.
}

\itodo{
  Ameen: lets add the above to the section. 
}

\item \label{Review.3.24}
Also, comparison with previous work done by (Zaraket ) 
in different vesion seems like comparing with your previous work 
only and not with others. 
It would be nice to compare others work too because user 
interface could be introduced in different view.

\answer{
  \framework targets entity and 
  relational entity extraction. 
  We are not aware and do not have access to other 
  previous work that performs morphology based relational entity 
  extraction for Arabic.
  We are open to perform such experiments in case the reviewers 
  can point us to such accessible tools. 
}

\item \label{Review.3.24}
What is the data size of your evaluation? 
I couldn't find how presion and recal was counted. 
you mentioned books but did you covered all the text in those 
books ? and how long was it? you can define it in term of 
number of relation extracted , tags added, expesion processed, 
sentences,..etc

\answer{
  We include more information about the data and 
  the evaluation process... 
}

\itodo{
  Answer.. 
}

\item \label{Review.3.24}
7- At section Discussion, I strongly urge you to discuss 
WHY the precision and recall have these values.

\answer{
We extend the discussion section to discuss ... 
}

\item \label{Review.3.25}
Clarity:  
It was not very clear how the work was done 
``Methodology part''. 
Section 4 ``MERF'' please add ``Methedology''.

\answer{
  We added a methodology section. 
}

\item \label{Review.3.25}
Having ``Existing annotation and entity extraction tools'' 
under unspecified section is misleading the reader. 
unnumbered subsections was misleading me as a reader.

\answer{
  Fixed. CLS file was not compatible with arabtex package. 
}

\item \label{Review.3.25}
table 1 at page 7 while referring to it only at page 9. 
I think it needs to be closer to where it was mentioned in the text.

\answer{
  Done.
}

\itodo{
  Make sure this is moved. 
}

\item \label{Review.3.25}
``MERF regular expressions support operators such as concatenation, zero or one, zero or more, one or more, up to $M$” what is M? 
it could be for example 0<=M<=|chunk|

\answer{
  We clarify the 
  notation ``up to $M$'' in the paper to be as follows. 
  \begin{quote}
   up to $M$ repititions where $M$ is 
   a non-zero positive integer 
  \end{quote}
}

\item \label{Review.3.25}
Correctness: 
1- in the abstract, the sentence ``These techniques and 
tools require expertise in linguistics and programming and 
lack support of Arabic morphological analysis which is key to 
process Arabic text''
gives the meaning that ``it require lack support'' so I think it 
needs to be reformulated

\answer{
  We rephrased the sentence.
}

\item \label{Review.3.25}
2-``defines tag types and''.// unify the font here and 
many other places in the paper. 
for example look at words(,correct,commercial)

\answer{
  We use italics to emphasize important 
  concepts that we introduce for the first time. 
  We reduced the use of emphasize in the paper. 
}

\item \label{Review.3.25}
Originality:  
This work will contribute in facilitating Arabic corpus 
annotation, if it was made available for other researchers in 
the field to access and use it, although there is no 
referencing to where it can be accessed. 
this is an improvement of a per-existing work ``MATAr: Morphology-based Tagger for Arabic''

\answer{
\framework is open source and available online. We modified the
contributions in the Introduction Section to indicate that. 
}

### 2018-04-12 tex/merf/TALMajor/introduction.tex
changes to answer, colors, and some reviewers addressed

We illustrate the target of \framework using a simple example.
Consider the text in Figure~\ref{fig:intromotiv} which contains
directions to Dubai Mall~\footnote{text taken from the Dubai Mall website
~\url{http://www.thedubaimall.com/ar/}}.
The figure also presents a transliteration and an English translation of the Arabic text.
The framed words in the text are entities referring to names of people 
($n_1,n_2,n_3$), 
names of places ($p_1,\dots,p_7$), 
relative positions ($r_1,\dots,r_4$), 
and numerical terms ($u_1,u_2$). 
We would like to extract those entities, and then extract
the relational entities forming the graph in Figure~\ref{fig:intromotiv} 
where vertices express entities, 
and edges represent the relational entities.
\framework allows a regular user to do that interactively
in four phases that include morphological analysis, 
entity extraction based on morphological features, 
relational entity extraction, and entity cross-reference.

\framework regular expressions support operators such as concatenation, 
zero or one, zero or more, one or more, up to $M\in\mathbb{N}^+$, and logical conjunction and disjunction.
An editor allows the user to associate an action with each sub-expression.
The user specifies the action with C++ code and uses an API to access information related to the matches such as text, position, length, morphological features, and numerical value.

@@

In \framework, we make the following contributions.
\begin{itemize}
  \item \framework enables the user to define relations in a simple manner
    and automatically detects relational entities matching the user defined relations. 
  \item \framework enables the user to associate sub-expressions
    with code actions, and executes the code action 
    when a corresponding match is found.
    It also provides an API to enable access to match 
    features such as text, position, length, numerical value, and morphological features.
  \item \framework enables the user to tag words based on a synonymic relation using the $Syn^k$ feature.
\end{itemize}

>>>>

We illustrate the target of \framework using a simple example.
Consider the text in Figure~\ref{fig:intromotiv} which contains
directions to Dubai Mall~\footnote{text taken from the Dubai Mall website
~\url{http://www.thedubaimall.com/ar/}}.
\major{
The figure also presents a transliteration and an English translation of 
the Arabic text.
}
The framed words in the text are entities referring to names of people 
($n_1,n_2,n_3$), 
names of places ($p_1,\dots,p_7$), 
relative positions ($r_1,\dots,r_4$), 
and numerical terms ($u_1,u_2$). 
We would like to extract those entities, and then extract
the relational entities forming the graph in Figure~\ref{fig:intromotiv} 
where vertices express entities, 
and edges represent the relational entities.
\framework allows a regular user to do that interactively
in four phases that include morphological analysis, 
entity extraction based on morphological features, 
relational entity extraction, and entity cross-reference.

\framework regular expressions support operators such as concatenation, 
zero or one, zero or more, one or more, up to $M$ \major{repititions where $M$ is 
a non-zero positive integer}, and logical conjunction and disjunction.
An editor allows the user to associate an action with each sub-expression.
The user specifies the action with C++ code and uses an API to access information related to the matches such as text, position, length, morphological features, and numerical value.

@@

In \framework, we make the following contributions.
\begin{itemize}
  \item \framework enables the user to define relations in a simple manner
    and automatically detects relational entities matching the user defined relations. 
  \item \framework enables the user to associate sub-expressions
    with code actions, and executes the code action 
    when a corresponding match is found.
    It also provides an API to enable access to match 
    features such as text, position, length, numerical value, and morphological features.
  \item \framework enables the user to tag words based on a 
    \major{
    novel ligh Arabic wordnet relation that leverages the 
    synonym $Syn^k$ feature.
  }

  \item \major{
\framework is open source and available online for the research community 
    under on (\url{https://github.com/codelogicanalysis/atmine}).}
\end{itemize}

### 2018-04-12 tex/merf/TALMajor/relatedwork.tex
changes to answer, colors, and some reviewers addressed

Another track in the literature targets specific tasks such as NER using statistical machine learning techniques \cite{benajiba2007anersys,benajiba2008arabic,ekbal2010named,abdelrahman2010integrated}.
%The work in~\cite{ekbal2010named} presents a language independent approach for NER extraction using {\em support vector machines}. 
%The work in~\cite{abdelrahman2010integrated} integrates a semi-supervised bootstrapping pattern recognition technique, and a supervised classifier based on {\em conditional random fields} to solve NER problems.
Knowledge-based techniques such 
as~\cite{zaghouani2010adapting,traboulsi2009arabic} propose local grammars with morphological stemming.% to perform NER. 
%The work in~
\cite{ZaMaHaCicling2012Entity} present a method for extracting entities and events, and relations amongst them from Arabic text using a hierarchy of manually built 
finite state machines driven by morphological features, 
and graph transformation algorithms. 
Such techniques require advanced linguistic and programming expertise.

@@

Researchers also proposed systems for automatic IE based 
on user specifications. 
CPSL is a common pattern specification language for finite-state 
grammar~\cite{appelt1998common}. 
%\framework is an extension to CPSL with action execution and relation construction. 
%It defines three sections for declaration, rule definition, and macros. 
The work in \cite{chiticariu2010systemt} presents SystemT, a system based on 
an algebraic Approach to Declarative information extraction (IE). 
%It uses a declarative rule language and an optimizer. 
TEXTMARKER is a rule-based IE system designed to extract structured data from 
text \cite{atzmueller2008rule}. 
\cite{urbain2012user} presents a user-driven relational model 
requiring a user natural language query to extract entities and relational entities.
\end{comment}

>>>>

\major{
Another track in the literature targets specific tasks such as NER using 
statistical and machine learning techniques such as maximum entropy, 
optimized feature sets and conditional random fields~\cite{benajiba2007anersys,benajiba2008arabic,ekbal2010named,abdelrahman2010integrated}.
}
%The work in~\cite{ekbal2010named} presents a language independent approach for NER extraction using {\em support vector machines}. 
%The work in~\cite{abdelrahman2010integrated} integrates a semi-supervised bootstrapping pattern recognition technique, and a supervised classifier based on {\em conditional random fields} to solve NER problems.
Knowledge-based techniques such 
as~\cite{zaghouani2010adapting,traboulsi2009arabic} propose local grammars with morphological stemming.% to perform NER. 
%The work in~
\cite{ZaMaHaCicling2012Entity} present a method for extracting entities and events, and relations amongst them from Arabic text using a hierarchy of manually built 
finite state machines driven by morphological features, 
and graph transformation algorithms. 
Such techniques require advanced linguistic and programming expertise.

@@

Researchers also proposed systems for automatic IE based 
on user specifications. 
CPSL is a common pattern specification language for finite-state 
grammar~\cite{appelt1998common}. 
%\framework is an extension to CPSL with action execution and relation construction. 
%It defines three sections for declaration, rule definition, and macros. 
The work in~\cite{chiticariu2010systemt} presents SystemT, a system based on 
an algebraic Approach to Declarative information extraction (IE). 
%It uses a declarative rule language and an optimizer. 
TEXTMARKER is a rule-based IE system designed to extract structured data from 
text \cite{atzmueller2008rule}. 
\cite{urbain2012user} presents a user-driven relational model 
requiring a user natural language query to extract entities and relational entities.
\end{comment}
